A comparison of design-based and model-based approaches for finite population spatial data.

### 2021-12-08 inst/manuscript/manuscript.Rmd
minor updates using plot_grid

```{r figdata, out.width = "49%", fig.cap = "Population distribution of mercury concentration (hg) for 986 lakes in the contiguous United States in a spatial layout (left) and a histogram (right).", message = FALSE, warning = FALSE, fig.show='hold', fig.align='center'}
merc <- ggplot(data = nla_nomiss_both, aes(x = total_hg)) +
  geom_histogram(colour = "black", fill = "white", bins = 15) +
  labs(x = "HG (ng / g)")
# dist <- ggplot(data = nla_nomiss_both, aes(x = RDis_IX)) +
#   geom_histogram(colour = "black", fill = "white", bins = 15) +
#   labs(x = "Lakeshore Disturbance")
merc_map <- ggplot(data = nla_nomiss_both, aes(x = xcoords, y = ycoords)) +
  geom_point(aes(colour = total_hg)) +
  scale_colour_viridis_c() +
  labs(x = "", y = "", colour = "Hg") +
  lims(x = c(0, 6500)) +
  coord_quickmap() +
  theme_bw(base_size = 20) + 
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      legend.position = c(0.85, 0.5),
      legend.key.size = unit(0.75, "cm"))

merc_hist <- ggplot(data = nla_nomiss_both, aes(x = total_hg)) +
  geom_histogram(bins = 50) + 
  labs(x = "Hg", y = "Count") +
  theme_bw(base_size = 20)

merc_map
merc_hist
```

@@

```{r figsv, out.width = "85%", fig.align='center', fig.cap = "The empirical semivariogram (black circles) of mercury concentration against the REML fit using the estimated covariance parameters (black line) from GRTS-Model."}
plot(mod_grts)
```

>>>>

```{r, message = FALSE, warning = FALSE}
merc <- ggplot(data = nla_nomiss_both, aes(x = total_hg)) +
  geom_histogram(colour = "black", fill = "white", bins = 15) +
  labs(x = "HG (ng / g)")
# dist <- ggplot(data = nla_nomiss_both, aes(x = RDis_IX)) +
#   geom_histogram(colour = "black", fill = "white", bins = 15) +
#   labs(x = "Lakeshore Disturbance")
merc_map <- ggplot(data = nla_nomiss_both, aes(x = xcoords, y = ycoords)) +
  geom_point(aes(colour = total_hg)) +
  scale_colour_viridis_c() +
  labs(x = "", y = "", colour = "Hg") +
  # lims(x = c(0, 6500)) +
  coord_quickmap() +
  theme_bw(base_size = 20) + 
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank())#,
      #legend.position = c(0.85, 0.5),
      #legend.key.size = unit(0.75, "cm"))

merc_hist <- ggplot(data = nla_nomiss_both, aes(x = total_hg)) +
  geom_histogram(bins = 50) + 
  labs(x = "Hg", y = "Count") +
  theme_bw(base_size = 20)
```

```{r, warning = FALSE, message = FALSE, include = FALSE}
mod_plot <- plot(mod_grts) +
  labs(x = "Distance", title = "") +
  scale_size_continuous(name = "Pairs") +
  theme_bw(base_size = 20)
```

```{r figdata, out.width = "100%", fig.cap = "Population distribution of mercury concentration (hg) for 986 lakes in the contiguous United States in a spatial layout (left) and a histogram (right). The empirical semivariogram (black circles) of mercury concentration against the REML fit using the estimated covariance parameters (black line) from GRTS-Model.", message = FALSE, warning = FALSE, fig.align='center'}
plot_grid(merc_map, plot_grid(merc_hist, mod_plot), ncol = 1, nrow = 2)
# plot_grid(merc_map, merc_hist, mod_plot, nrow = 3)
```

@@

### 2021-12-08 inst/manuscript/manuscript.tex
minor updates using plot_grid

{\centering \includegraphics[width=0.49\linewidth]{manuscript_files/figure-latex/figdata-1} \includegraphics[width=0.49\linewidth]{manuscript_files/figure-latex/figdata-2}

@@

\caption{Population distribution of mercury concentration (hg) for 986 lakes in the contiguous United States in a spatial layout (left) and a histogram (right).}\label{fig:figdata}
\end{figure}

@@

{\centering \includegraphics[width=0.85\linewidth]{manuscript_files/figure-latex/figsv-1}

\caption{The empirical semivariogram (black circles) of mercury concentration against the REML fit using the estimated covariance parameters (black line) from GRTS-Model.}\label{fig:figsv}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figdata-1}

@@

\caption{Population distribution of mercury concentration (hg) for 986 lakes in the contiguous United States in a spatial layout (left) and a histogram (right). The empirical semivariogram (black circles) of mercury concentration against the REML fit using the estimated covariance parameters (black line) from GRTS-Model.}\label{fig:figdata}
\end{figure}

@@
